An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-06 Manuscript.tex
manuscript development

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={Ouafaa Hmaddi1},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{The title}
\author{Ouafaa Hmaddi\textsuperscript{1}}
\date{}

@@

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

@@

Correspondence concerning this article should be addressed to Ouafaa Hmaddi, Postal address. E-mail: \href{mailto:ohmaddi@uoregon.edu}{\nolinkurl{ohmaddi@uoregon.edu}}

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{lme4} (Version 1.1.23; Bates, Mächler, Bolker, \& Walker, 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), and \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

@@

@@

@@

@@

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$z\$\\
\hline
Intercept & -1.47 & 0.08 & -19.16\\
\hline
Attention to Human capital(AHC) & 0.10 & 0.08 & 1.24\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$z\$\\
\hline
Intercept & -0.94 & 0.53 & -1.77\\
\hline
AHC & 0.86 & 0.44 & 1.97\\
\hline
Ease of finding skilled employees & -0.12 & 0.12 & -0.96\\
\hline
AHCxEase of finding skilled employees & -0.16 & 0.09 & -1.69\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$t\$\\
\hline
Intercept & 738.20 & 485.65 & 1.52\\
\hline
Attention to Human capital & 2,841.44 & 2,153.75 & 1.32\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$t\$\\
\hline
Intercept & -1,882.79 & 3,470.12 & -0.54\\
\hline
AHC & -9,744.87 & 16,027.75 & -0.61\\
\hline
Ease of finding skilled employees & 618.05 & 783.89 & 0.79\\
\hline
AHCxEase of finding skilled employees & 2,989.85 & 3,687.09 & 0.81\\
\hline
\end{tabular}

@@

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: participated ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14831.2  14869.8  -7410.6  14821.2    16439 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.3463 -0.5096 -0.4046 -0.2890  2.4564 
## 
## Random effects:
##  Groups   Name                          Variance Std.Dev. Corr 
##  country  (Intercept)                   0.008936 0.09453       
##           accel_ben_rank_direct_funding 0.001665 0.04080  -0.49
##  Residual                               0.142950 0.37809       
## Number of obs: 16444, groups:  country, 83
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)  0.19651    0.01228   16.01
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ425 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14620.0  14681.5  -7302.0  14604.0    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.4017 -0.5138 -0.3955 -0.2813  2.4249 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0085583 0.09251       
##           accel_ben_rank_direct_funding 0.0009436 0.03072  -1.00
##  Residual                               0.1432556 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                         Estimate Std. Error t value
## (Intercept)                            0.2004428  0.0710787   2.820
## accel_ben_rank_direct_funding         -0.0255510  0.0455072  -0.561
## EOSQ425                                0.0008104  0.0184340   0.044
## accel_ben_rank_direct_funding:EOSQ425 -0.0023544  0.0107909  -0.218
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__ -0.490              
## EOSQ425     -0.984  0.485       
## a____:EOSQ4  0.533 -0.975 -0.545
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ089 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14619.7  14681.2  -7301.8  14603.7    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.4020 -0.5136 -0.3962 -0.2810  2.4270 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0084870 0.09212       
##           accel_ben_rank_direct_funding 0.0009291 0.03048  -1.00
##  Residual                               0.1432565 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                        Estimate Std. Error t value
## (Intercept)                            0.229561   0.046331   4.955
## accel_ben_rank_direct_funding         -0.037525   0.030596  -1.226
## EOSQ089                               -0.008695   0.014873  -0.585
## accel_ben_rank_direct_funding:EOSQ089  0.001088   0.008465   0.129
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__ -0.477              
## EOSQ089     -0.961  0.464       
## a____:EOSQ0  0.539 -0.944 -0.566
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14619.7  14681.2  -7301.8  14603.7    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.3992 -0.5115 -0.3980 -0.2807  2.4272 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0085682 0.09256       
##           accel_ben_rank_direct_funding 0.0009053 0.03009  -1.00
##  Residual                               0.1432523 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                              Estimate Std. Error t value
## (Intercept)                                 2.113e-01  2.084e-02  10.137
## accel_ben_rank_direct_funding              -3.313e-02  1.549e-02  -2.139
## DOMCREDITGDP                               -1.339e-04  2.829e-04  -0.473
## accel_ben_rank_direct_funding:DOMCREDITGDP -1.288e-05  1.590e-04  -0.081
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ DOMCRE
## accl_bn_r__ -0.414              
## DOMCREDITGD -0.788  0.334       
## a____:DOMCR  0.441 -0.768 -0.567
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  628881.3  628919.9 -314435.7  628871.3     16439 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.756  -0.010  -0.008  -0.004 126.757 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   1.168e+13  3417674      
##           accel_ben_rank_direct_funding 4.366e+13  6607224 -1.00
##  Residual                               2.373e+15 48709324      
## Number of obs: 16444, groups:  country, 83
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)   607877     562167   1.081
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An institutional approach to attention allocation and venture resource mobilization and acquisition},
  pdfauthor={Ouafaa Hmaddi1},
  pdfkeywords={attention, resources, institutional capital, accelerators},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{An institutional approach to venture attention allocation}
\keywords{attention, resources, institutional capital, accelerators}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{An institutional approach to attention allocation and venture resource mobilization and acquisition}
\author{Ouafaa Hmaddi\textsuperscript{1}}
\date{}

@@

Lundquist College of Business

Department of Management

@@

Correspondence concerning this article should be addressed to Ouafaa Hmaddi, 292A Anstett. E-mail: \href{mailto:ohmaddi@uoregon.edu}{\nolinkurl{ohmaddi@uoregon.edu}}

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Early stage entrepreneurs are faced with a range of resource choices to seek, and must decide what should garner their attention. The literature on entrepreneurial resources argues the resources entrepreneurs possess shape their resource acquisition and once they raise one resource others follow. Thus, one might theorize that founders should focus their attention on the resource they can leverage based on their existing resource endowment. However, resource acquisition depends on both entrepreneurs' resource endowment and the institutional-level capital. Both are indispensable antecedents that affect the mobilization and acquisition of additional capital.

The value of a resource varies with its institutional context (Holburn \& Zelner, 2010). On the one hand, strong institutions can increase the value of a resource by streamlining access to complementary external resources (Khanna \& Rivkin, 2001; North \& others, 1990). For example, in countries with strong financing infrastructure, acquiring financing can streamline accessing other resources and thus it would make sense to focus on raising capital at venture's earliest stages. On the other hand, resources such as legitimation or social capital can substitute for the weak institutions and capital infrastructure, thereby increasing in value when institutions are weak (Khanna \& Palepu, 1997; Kock \& Guillén, 2001). Therefore, the broader environment can enhance or inhibit the optimal use of the endowed resource capital. I posit that an examination of both the venture and its broader institutional environment would give us more insights about where founders attention should be allocated. Specifically, I hypothesize that the institutional-level capital positively moderates the relationship between a founder's attention and its subsequent resource mobilization and acquisition. For example, attention to human capital is more positively related to a higher number of employees in contexts in which it has higher intuitional-level human capital. This similarly applies to social capital, and financial capital as the types of resources sought by entrepreneurs. Thus, in this paper I seek to examine the following research question: How does the alignment of the institutional context and the allocation of entrepreneurial attention toward specific resources influence the venture's resource mobilization and acquisition?

\hypertarget{hypotheses-development}{%
\section{Hypotheses Development}\label{hypotheses-development}}

At the heart of the intersection between resource acquisition and the institutional context is entrepreneurial attention, that is, founders' attention allocation to resources. Bounded by their limited attentional capacities, entrepreneurs cannot attend to all the resources; rather, they focus on some resources but must ignore others. Where they focus their attention determines the propensity of mobilizing and acquiring resources. A venture could miss the chance to exploit an opportunity of resources acquisition if that opportunity never appears on the entrepreneur's radar screens because they are too focused on an alternative resource. For example, a voluntary work with potential partners who are well connected to other investors might be missed because the founder is too focused on raising capital by honing their business plan over and over and even paying accounting boutique firms to develop that business plan for them.

Thus, selective attention plays a crucial role in both individual and organizational behavior because it bounds individual rationality and determines the menu of available actions (Simon, 1947). The debate over which resource should garner the entrepreneur's attention concludes that the founding team resource endowment is the key factor that influences resource acquisition. For instance, scholars argue that founding teams with a more ties to potential investors are more likely to gain funding (Shane \& Stuart, 2002). Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital (e.g.; (Hochberg, Ljungqvist, \& Lu, 2007)) we would expect that early-stage financing should be most likely to garner founders' attention. However, the role of the institutional context has been ignored and neglected in this debate. I argue that selective attention allocation depends on both entrepreneur's resource endowment and institutional capital.

Therefore, I state the following hypotheses about the relationship between the congruence level of the entrepreneurs' attention to resources and the institutional level capital, and the venture's resource mobilization, acquisition, and performance.

\textbf{Hypothesis 1} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the odds of mobilization that resource}

\textbf{Hypothesis 2} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the level of the accumulated resource}

\textbf{Hypothesis 3} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the venture performance}

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

@@

I used R (Version 4.0.2; R Core Team, 2020b) and the R-packages \emph{caret} (Version 6.0.86; Kuhn, 2020), \emph{dplyr} (Version 1.0.0; Wickham et al., 2020), \emph{EFAutilities} (Version 2.0.0; Zhang, Jiang, Hattori, \& Trichtinger, 2019), \emph{forcats} (Version 0.5.0; Wickham, 2020), \emph{foreign} (Version 0.8.80; R Core Team, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{haven} (Version 2.3.1; Wickham \& Miller, 2020), \emph{janitor} (Version 2.0.1; Firke, 2020), \emph{knitr} (Version 1.29; Xie, 2015), \emph{lattice} (Version 0.20.41; Sarkar, 2008), \emph{lme4} (Version 1.1.23; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.2; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{lubridate} (Version 1.7.9; Grolemund \& Wickham, 2011), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{plm} (Version 2.2.3; Croissant \& Millo, 2008; Millo, 2017), \emph{plot3D} (Version 1.3; Soetaert, 2019), \emph{preprocessCore} (Version 1.50.0; Bolstad, 2020), \emph{psych} (Version 1.9.12.31; Revelle, 2019), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{reshape2} (Version 1.4.4; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{sjPlot} (Version 2.8.4; Lüdecke, 2020), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.3; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.0; Wickham \& Henry, 2020), \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019), and \emph{XLConnect} (Version 1.0.1; Mirai Solutions GmbH, 2020) for all our analyses.

@@

\#\#Control variables

\#\#Constrcuting human capital index (control variable)
\#\#\#Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding

\#\#Gender decomposition variable

@@

\#Distribution of attention

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-2.pdf}

\#\#Outcomes

@@

\#Predictor and outcome plots
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-2.pdf}

@@

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $z$\\
\hline
Intercept & -1.46 & 0.08 & -19.18\\
\hline
Attention to Human capital(AHC) & 0.11 & 0.07 & 1.54\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $z$\\
\hline
Intercept & -0.85 & 0.53 & -1.61\\
\hline
AHC & 0.92 & 0.45 & 2.05\\
\hline
Ease of finding skilled employees & -0.14 & 0.12 & -1.14\\
\hline
AHCxEase of finding skilled employees & -0.17 & 0.10 & -1.79\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $t$\\
\hline
Intercept & 762.25 & 502.25 & 1.52\\
\hline
Attention to Human capital & 2,955.97 & 2,238.11 & 1.32\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & $b$ & SE & $t$\\
\hline
Intercept & -1,955.91 & 3,599.05 & -0.54\\
\hline
AHC & -10,174.65 & 16,704.03 & -0.61\\
\hline
Ease of finding skilled employees & 641.03 & 813.08 & 0.79\\
\hline
AHCxEase of finding skilled employees & 3,118.93 & 3,842.90 & 0.81\\
\hline
\end{tabular}

@@

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14773.7  14812.1  -7381.8  14763.7    15976 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0388 -0.4890 -0.4207 -0.3515  3.0479 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.300861 0.54851       
##          accel_ben_rank_direct_funding 0.007982 0.08934  -1.00
## Number of obs: 15981, groups:  country, 82
## 
## Fixed effects:
##                               Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                   -1.45326    0.07722 -18.821  < 2e-16 ***
## accel_ben_rank_direct_funding -0.19333    0.06321  -3.059  0.00222 ** 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr)
## accl_bn_r__ -0.171
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ425 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14562.1  14615.8  -7274.1  14548.1    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0463 -0.4908 -0.4210 -0.3513  3.0165 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.287438 0.53613       
##          accel_ben_rank_direct_funding 0.009936 0.09968  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                        Estimate Std. Error z value Pr(>|z|)   
## (Intercept)                           -1.349694   0.434021  -3.110  0.00187 **
## accel_ben_rank_direct_funding         -0.210801   0.285396  -0.739  0.46013   
## EOSQ425                               -0.021755   0.112408  -0.194  0.84654   
## accel_ben_rank_direct_funding:EOSQ425  0.003382   0.065751   0.051  0.95898   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__ -0.246              
## EOSQ425     -0.983  0.246       
## a____:EOSQ4  0.280 -0.974 -0.289
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ089 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14561.6  14615.2  -7273.8  14547.6    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0482 -0.4904 -0.4209 -0.3510  3.0323 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.284084 0.53299       
##          accel_ben_rank_direct_funding 0.009676 0.09837  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                       Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                           -1.21998    0.28033  -4.352 1.35e-05 ***
## accel_ben_rank_direct_funding         -0.24283    0.19650  -1.236    0.217    
## EOSQ089                               -0.07084    0.09006  -0.787    0.432    
## accel_ben_rank_direct_funding:EOSQ089  0.01463    0.05184   0.282    0.778    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__ -0.232              
## EOSQ089     -0.960  0.230       
## a____:EOSQ0  0.281 -0.944 -0.300
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14561.8  14615.5  -7273.9  14547.8    15720 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.0466 -0.4909 -0.4213 -0.3514  3.0629 
## 
## Random effects:
##  Groups  Name                          Variance Std.Dev. Corr 
##  country (Intercept)                   0.289392 0.53795       
##          accel_ben_rank_direct_funding 0.009926 0.09963  -1.00
## Number of obs: 15727, groups:  country, 73
## 
## Fixed effects:
##                                              Estimate Std. Error z value
## (Intercept)                                -1.3735020  0.1256629 -10.930
## accel_ben_rank_direct_funding              -0.2051438  0.1031016  -1.990
## DOMCREDITGDP                               -0.0010317  0.0017273  -0.597
## accel_ben_rank_direct_funding:DOMCREDITGDP  0.0001439  0.0009667   0.149
##                                            Pr(>|z|)    
## (Intercept)                                  <2e-16 ***
## accel_ben_rank_direct_funding                0.0466 *  
## DOMCREDITGDP                                 0.5503    
## accel_ben_rank_direct_funding:DOMCREDITGDP   0.8817    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ DOMCRE
## accl_bn_r__ -0.193              
## DOMCREDITGD -0.778  0.159       
## a____:DOMCR  0.233 -0.779 -0.313
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  541645.1  541683.5 -270817.5  541635.1     15976 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.316  -0.040  -0.029  -0.018 120.803 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr
##  country  (Intercept)                   1.187e+11  344600      
##           accel_ben_rank_direct_funding 2.332e+09   48286  1.00
##  Residual                               3.062e+13 5533830      
## Number of obs: 15981, groups:  country, 82
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)   226024      79869    2.83
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}
